A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Elaborate on DBpedia
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1066 43ef1190-90fd-4dd7-a769-d0121f02b80e
RDF::Endpoint is in there
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1067 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl module
RDF::LinkedData\footnote{See
  \url{https://metacpan.org/pod/RDF::LinkedData}. It is also present
  in Debian/Ubuntu as \texttt{librdf-linkeddata-perl}}, which is
developed by and runs on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in the companion technical report
\cite{kjernsmo_add_survey_2015}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints.\todo{elaborate}

>>>>

\todo{overview of characteristics and why}

@@

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which are partly
developed by and runs on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in the companion technical report
\cite{kjernsmo_add_survey_2015}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints. DBPedia has historically been updated
only a few times a year, but this was probably chosen so as to not
make a commitment long into the future. It may provide considerable benefits.
